%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{acknowledgements}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}

\def\thanks#1{%
\begingroup
\leftskip1em
\noindent #1
\par
\endgroup
}

\section*{Acknowledgments}
I would like to thank my supervisors \textbf{William Spataro} and \textbf{Donato D'Ambrosio} for their invaluable support and encouragement and for believing in me from the beginning of this  Ph.D. I really wish every Ph.D. student in the world have supervisors like them. 
I would also like to thank \textbf{Alessio De Rango} and \textbf{Paola Arcuri} who were of invaluable help and for being such a great study partners.

I would like to thank \texttt{NVIDIA} corporation for providing the \textit{GTX980 GPU}
and \textit{Tesla K40} coprocessor I have used to carry out my research.

I would also like to thank also to \textbf{Prof. Filippo Melascina} from the Institute of BioEngineering of the University of Edinburgh (UK) who kindly gave access to the microscopy equipment and to \textbf{Alice Mari} who was of great help in providing the experimental raw data and subsequently in analyzing the results obtained in chapter \ref{ch:bacteria}.

I would also like to thank \textbf{Prof. Jin Ooi} for giving the opportunity to being a research visiting student at the University of Edinburgh for 10 months (October 2016 - July 2017) working on the VELaSSCO EU project and, \textbf{Prof. Gihan R. Mudalige}, who supervised me during a three months visiting period (June- September 2017) at University of Warwick, while I was investigating a novel MPI implementation of an algorithm for solving tridiagonal linear systems within the context of the OPS framework.

I would also like to thanks all the people who I have met during these years and from which I have learned and, with whom I have enjoyed together, so many things.

A special thank to all friends, especially to \textbf{Vincenzo Curti}  with whom I have shared so many important moments during this journey.

\endgroup
